Job Demands-Resources model components through the lens of O*NET classifications

### 2022-07-21 SIOP_Onet_FA.Rmd
FA with 2, 7, 8, 9 factors

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

@@

# Discussion

>>>>

@@

```{r eight_factorFA}
##Here's where we started - it appears that based on scree plot, 8 factors might be appropriate.
efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
summary(efa)

together <- cbind(data, efa$scores)

#res.cor <- correlate(together[c(405:413)], use="pairwise.complete.obs")
#res.cor %>% fashion()
#res.cor %>% shave(upper=FALSE) %>% rplot()

efa$loadings
print(efa$loadings,cut=.3,digits=2)
```

```{r two_factorFA}
##Next, trying the 2 overarching factors we noted first:
efa <- fa(forfa, rotate="oblimin", nfactors=2, n.obs=568, scores=TRUE, alpha=.1)
summary(efa)

efa$loadings
print(efa$loadings,cut=.3,digits=2)
```

```{r seven_factorFA}
## Try 7 factor solution next. 
efa <- fa(forfa, rotate="oblimin", nfactors=7, n.obs=568, scores=TRUE, alpha=.1)
summary(efa)

efa$loadings
print(efa$loadings,cut=.3,digits=2)
```

```{r nine_factorFA}
## Try 9 factor solution next. 
efa <- fa(forfa, rotate="oblimin", nfactors=9, n.obs=568, scores=TRUE, alpha=.1)
summary(efa)

efa$loadings
print(efa$loadings,cut=.3,digits=2)
```
# Discussion
